Convex Surrogates via Polyhedral Losses

### 2019-05-04 notes/bo-separated.tex
starting on new proof

@@

Let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\Gamma(p) : p \in \Delta_{\Y}\}$.
In other words, for each $p$, we take the set of optimal reports $R = \Gamma(p) \subseteq \R$, and we add $R$ to $\S$.

Given a fixed embedding, for each report $r \in \R$, let $u_r \in \R'$ denote its embedding point.
Given a set $R \subseteq \R$, let $U_R = \{u_r : r \in \R\}$.

>>>>

Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.

@@

We are given an original loss $\ell$ with property $\gamma$ and finite report space $\R$; and a polyhedral embedding with loss $L$, property, $\Gamma$, and embedding points $\{u_r : r \in \R\}$.

For each report $r \in \R$, let $u_r$ denote its embedding point.

Let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\S$.

Let $\mathcal{U} \subseteq 2^{\reals^d}$ be defined as $\mathcal{U} = \{\Gamma(p) : p \in \Delta_{\Y}\}$.

\begin{lemma} \label{lemma:U-convex-closed}
  Each element $U$ of $\mathcal{U}$ is a closed, convex set.
\end{lemma}
\begin{proof}
  \bo{TODO - minimizers of polyhedral loss}
\end{proof}

\begin{lemma} \label{lemma:U-biject}
  There is a bijection between $\mathcal{S}$ and $\mathcal{U}$ where $R \leftrightarrow U$ if and only if $\gamma(p) = R$ and $\Gamma(p) = U$ for some $p$.
  In this case $U$ contains $u_r$ if and only if $r \in R$.
\end{lemma}
\begin{proof}
  \bo{TODO!}
\end{proof}

\begin{lemma} \label{lemma:U-separated}
  Let $\{U_j : j \in \mathcal{J}\} \subseteq \mathcal{U}$ be a subset of $\mathcal{U}$.
  Then one and only one of the following is true:
  \begin{enumerate}
    \item The intersection of the family is nonempty, i.e. they all overlap at some point.
    \item There exists $\epsilon > 0$ such that, for each member $U_j$, we have $d(U, \cap_{j' \neq j} U_{j'}) \geq \epsilon$.
          In other words, each member is separated from the intersection of the others.
  \end{enumerate}
\end{lemma}
\begin{proof}
  \bo{TODO! This is the key one!}
\end{proof}

\begin{corollary} \label{cor:separated-small-enough}
  There is an $\epsilon > 0$ such that, for all families $\{U_j : j \in \mathcal{J}\}$ that do not intersect at a point, each member is separated from the intersection of the others by more than $2\epsilon$.
\end{corollary}
\begin{proof}
  Take the minimum $\epsilon$ promised by Lemma \ref{lemma:U-separated}, over all finite subsets of $\mathcal{U}$, and divide by $3$.
\end{proof}

\begin{lemma}
  If a subset of $\mathcal{U}$ intersect at some point, then their corresponding $R$ sets all intersect.
\end{lemma}

\begin{theorem}
  Let $L(u,y)$ be a surrogate loss for $\ell(r,y)$ for which there exists some calibrated link.
  Suppose $L$ is a polyhedral loss.
  Then there exists a calibrated, \emph{separated} link $\psi$ between these losses, meaning, for all $p$,
    \[ \inf_{u \in \R' : \psi(u) \not\in \gamma(p)} L(u;p) > \inf_{u \in \R'} L(u;p) . \]
\end{theorem}
\begin{proof}
We construct $\psi$.

Fix a small enough $\epsilon$ as promised by Lemma \ref{lemma:U-separated}.

Now, we apply the following iterative procedure.
For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-separated}).
For every $u \in B\left(U, \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.

%(Geometrically: in the case where $R=\{r\}$, we simply assign the epsilon-ball around $u_r$ to point to only $r$. In the case with multiple reports in $R$, we take the polyhedron with corners $U_R$ and ``thicken it'', then require that this thick shape map only to elements of $R$.)

First: consider any $u \in \R'$.
If $u$ is not in $B(U,\epsilon)$ for any $U \in \mathcal{U}$, then we have $\Psi(u) = \R$, so it is nonempty.
Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family that contain $u$.
We have each $U_j \lefrightarrow R_j$ for some $R_j \subseteq \R$ and
  \[ \Psi(u) = \cap_{j \in \mathcal{J}} R_j . \]
Now, we claim that all $U_j$ intersect at some point.

Finally, we must show that $\psi$ is a separated, calibrated link.
\bo{TODO - should be the easy part!}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\break

{\large OLD STUFF -- MOVED HERE BY BO 2019-05-04 09:34 ET}

Given a set $R \subseteq \R$, let $U_R = \{u_r : r \in \R\}$.
